Age-related changes in plant growth and traits

### 2015-08-27 Accessory_figs.rmd
scripts now mostly working. Adding new information on costs of reproduction

###5. What influences the correlation between RA and plant size (or total reproductive investment)?
  ***Don't trust anything until I know RA and repro_inv are correct, because PHPH and PUTU have huge influence on patterns***
```{r, echo=FALSE,message=FALSE,fig.width=12, fig.height=30,warning=FALSE}
par(mfrow=c(5,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))

mod <- lm(RA~log(propagule_inv),data=subset(SummaryInd,RA>0&propagule_inv>0))
plot(propagule_inv~RA,data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to propagules (mg)")
words.top.left.logxy(mod)

mod <- lm(RA~prop_propagule,data=subset(SummaryInd,RA>0&prop_propagule>0))
plot(prop_propagule~RA,data=subset(SummaryInd,RA>0&prop_propagule>0), log="", pch=16,col=col.spp(species),ylab="propagules (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(RA~log(prepollen_aborted_inv),data=subset(SummaryInd,RA>0&prepollen_aborted_inv>0))
plot(prepollen_aborted_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="y",ylab="pre-pollination aborted tissues (mg)")
words.top.left.logxy(mod)

mod <- lm(RA~prop_prepollen_aborted,data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0))
plot(prop_prepollen_aborted~RA,data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0), pch=16,col=col.spp(species), log="",ylab="pre-pollination aborted tissues (as proportion repro inv)")
words.bottom.right.logx(mod)

mod <- lm(RA~log(prepollen_success_inv),data=subset(SummaryInd,RA>0&prepollen_success_inv>0))
plot(prepollen_success_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="y",ylab="pre-pollination successful tissues (mg)")
words.top.left.logxy(mod)

mod <- lm(RA~prop_prepollen_success,data=subset(SummaryInd,RA>0&prop_prepollen_success>0))
plot(prop_prepollen_success~RA,data=subset(SummaryInd,RA>0&prop_prepollen_success>0), pch=16,col=col.spp(species), log="",ylab="pre-pollination successful tissues (as proportion repro inv)")
words.bottom.right.logx(mod)

mod <- lm(RA~log(packaging_dispersal_inv),data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0))
plot(packaging_dispersal_inv~RA,data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to packaging and dispersal (mg)")
words.bottom.right.logxy(mod)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

mod <- lm(RA~prop_packaging_dispersal,data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0))
plot(prop_packaging_dispersal~RA,data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0), log="", pch=16,col=col.spp(species),ylab="packaging and dispersal (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(RA~log(postpollen_aborted_inv),data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0))
plot(postpollen_aborted_inv~RA,data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to tissues aborted postpollination (mg)")
words.bottom.right.logxy(mod)

mod <- lm(RA~prop_postpollen_aborted,data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0))
plot(prop_postpollen_aborted~RA,data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0), log="", pch=16,col=col.spp(species),ylab="tissues aborted postpollination (as proportion repro inv)")
words.bottom.left.logx(mod)
```

##6. Shifts in proportion to tissue types across species  
- Reasonably idiosyncratic patterns  
- Species very different in which accessory tissues they invest the most in - which reflects the differences in basic structure (i.e. Banksia cones), but also more subtlely that some species abort lots of buds (pre-pollination aborted), while other species abort more fully formed flowers   
- COER, EPMI, LEES, PILI invest the most energy in propagules  
- HATE invests by far the least into propagules  
```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=28,warning=FALSE}
par(mfrow=c(4,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2))  
mean1 <- SummarySpp[["mean"]]$prop_propagule
se1 <- SummarySpp[["sd"]]$prop_propagule
boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylab="proportion propagules",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$propagule_per_seed
se1 <- SummarySpp[["sd"]]$propagule_per_seed
boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylab="propagules",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$prop_prepollen_all
se1 <- SummarySpp[["sd"]]$prop_prepollen_all
boxplot(mean1~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylim=c(.1,1),ylab="pre-pollination tissues",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$prepollen_all_per_seed
se1 <- SummarySpp[["sd"]]$prepollen_all_per_seed
boxplot((.01+prepollen_all_per_seed)~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylab="pre-pollination tissues",xlab="",log="y")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$prop_packaging_dispersal
se1 <- SummarySpp[["sd"]]$prop_packaging_dispersal
boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="packaging and dispersal")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$packaging_dispersal_per_seed
se1 <- SummarySpp[["sd"]]$packaging_dispersal_per_seed
boxplot((packaging_dispersal_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="packaging and dispersal",log="y")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$prop_postpollen_aborted
se1 <- SummarySpp[["sd"]]$prop_postpollen_aborted
boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="aborted post-pollination tissues")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$postpollen_aborted_per_seed
se1 <- SummarySpp[["sd"]]$postpollen_aborted_per_seed
boxplot((postpollen_aborted_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="aborted post-pollination tissues",log="y")
se_function(mean1,se1)

>>>>

###5. What influences the correlation between RA and plant size (or total reproductive investment)?  
* we know bigger plants have higher RA - do all accessory tissue components shift equally or do some have greater proportional effects
* total energy to propagules increases with RA, because RA increases with plant size  
* relative investment in pre-pollination aborted tissues decreases with RA - but that energy is split across lots of different pools
* other regressions have significant slopes, but R^2 < .1, so not putting much meaning in them
```{r, echo=FALSE,message=FALSE,fig.width=12, fig.height=30,warning=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))

mod <- lm(RA~log(propagule_inv),data=subset(SummaryInd,RA>0&propagule_inv>0))
plot(propagule_inv~RA,data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to propagules (mg)")
words.bottom.right.logy(mod)

mod <- lm(RA~prop_propagule,data=subset(SummaryInd,RA>0&prop_propagule>0))
plot(prop_propagule~RA,data=subset(SummaryInd,RA>0&prop_propagule>0), log="", pch=16,col=col.spp(species),ylab="propagules (as proportion repro inv)")
words.bottom.left(mod)

mod <- lm(RA~log(prepollen_aborted_inv),data=subset(SummaryInd,RA>0&prepollen_aborted_inv>0))
plot(prepollen_aborted_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="y",ylab="pre-pollination aborted tissues (mg)")
words.bottom.right.logy(mod)

mod <- lm(RA~prop_prepollen_aborted,data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0))
plot(prop_prepollen_aborted~RA,data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0), pch=16,col=col.spp(species), log="",ylab="pre-pollination aborted tissues (as proportion repro inv)")
words.bottom.right(mod)

mod <- lm(RA~log(prepollen_success_inv),data=subset(SummaryInd,RA>0&prepollen_success_inv>0))
plot(prepollen_success_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="y",ylab="pre-pollination successful tissues (mg)")
words.bottom.right.logy(mod)

mod <- lm(RA~prop_prepollen_success,data=subset(SummaryInd,RA>0&prop_prepollen_success>0))
plot(prop_prepollen_success~RA,data=subset(SummaryInd,RA>0&prop_prepollen_success>0), pch=16,col=col.spp(species), log="",ylab="pre-pollination successful tissues (as proportion repro inv)")
words.bottom.right(mod)

mod <- lm(RA~log(packaging_dispersal_inv),data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0))
plot(packaging_dispersal_inv~RA,data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to packaging and dispersal (mg)")
words.bottom.right.logy(mod)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

mod <- lm(RA~prop_packaging_dispersal,data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0))
plot(prop_packaging_dispersal~RA,data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0), log="", pch=16,col=col.spp(species),ylab="packaging and dispersal (as proportion repro inv)")
words.bottom.left(mod)

mod <- lm(RA~log(postpollen_aborted_inv),data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0))
plot(postpollen_aborted_inv~RA,data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to tissues aborted postpollination (mg)")
words.bottom.right.logy(mod)

mod <- lm(RA~prop_postpollen_aborted,data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0))
plot(prop_postpollen_aborted~RA,data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0), log="", pch=16,col=col.spp(species),ylab="tissues aborted postpollination (as proportion repro inv)")
words.bottom.left(mod)
```

##6. Shifts in proportion to tissue types across species  
- Reasonably idiosyncratic patterns  
- Species very different in which accessory tissues they invest the most in - which reflects the differences in basic structure (i.e. Banksia cones), but also more subtlely that some species abort lots of buds (pre-pollination aborted), while other species abort more fully formed flowers   
- COER, EPMI, LEES, PILI invest the most energy in propagules  
- HATE invests by far the least into propagules  
```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=28,warning=FALSE}
par(mfrow=c(2,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2))  
mean1 <- SummarySpp[["mean"]]$prop_propagule
se1 <- SummarySpp[["se"]]$prop_propagule
boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylab="proportion propagules",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$propagule_per_seed
se1 <- SummarySpp[["se"]]$propagule_per_seed
boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylab="propagules",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$prop_prepollen_all
se1 <- SummarySpp[["se"]]$prop_prepollen_all
boxplot(mean1~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylim=c(.1,1),ylab="pre-pollination tissues",xlab="")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$prepollen_all_per_seed
se1 <- SummarySpp[["se"]]$prepollen_all_per_seed
boxplot((.01+prepollen_all_per_seed)~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylab="pre-pollination tissues",xlab="",log="y")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$prop_packaging_dispersal
se1 <- SummarySpp[["se"]]$prop_packaging_dispersal
boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="packaging and dispersal")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$packaging_dispersal_per_seed
se1 <- SummarySpp[["se"]]$packaging_dispersal_per_seed
boxplot((packaging_dispersal_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="packaging and dispersal",log="y")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$prop_postpollen_aborted
se1 <- SummarySpp[["se"]]$prop_postpollen_aborted
boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.005,1),ylab="aborted post-pollination tissues")
se_function(mean1,se1)

mean1 <- SummarySpp[["mean"]]$postpollen_aborted_per_seed
se1 <- SummarySpp[["se"]]$postpollen_aborted_per_seed
boxplot((postpollen_aborted_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="aborted post-pollination tissues",log="y")
se_function(mean1,se1)

### 2015-08-27 RA_figs.rmd
scripts now mostly working. Adding new information on costs of reproduction

plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
legend("bottomright",legend=labels.age(),col=col.age,pch=16, cex=.8,bty="n")
abline(0,1)
text(2.1,3,srt=45,"RA = 0.5")
abline(log10(3),1)
text(2,9,srt=45,"RA = 0.75")
abline(log10(9),1)
text(2,25,srt=45,"RA = 0.9")
abline(log10(19),1)
text(2,60,srt=45,"RA = 0.95")
abline(log10(.111),1)
text(19,3,srt=45,"RA = 0.1")
abline(log10(.010101),1)
text(170,2.4,srt=45,"RA = 0.01")
```

@@

@@

mtext("Vegetative investment (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
```
lmfits

###Calculating cost of reproduction as a growth deficit
```
par(mfrow=c(1,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
Summary2 <- SummaryInd
Summary2 <- merge(Summary2,select(results, -n), by=c("species"), all=TRUE)
Summary2$predict_growth <- ((Summary2$total_weight)*(10^(Summary2$b))) + (Summary2$a)
Summary2$cost <- Summary2$predict_growth - Summary2$growth_inv
Summary2$cost_plus_growth <- Summary2$cost + Summary2$growth_inv
plot(total_weight ~ cost_plus_growth,data=subset(Summary2),log="xy",col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
abline(0,1)

legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "cost"
xvar <- "repro_inv"

data <- subset(Summary2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
                    main=spp,col=col.age(data[[spp]]$age))
  abline(0,1)                  
}

mtext("Growth deficit (mg)", 2, outer=TRUE,cex=1.2)
mtext("Reproductive investment (mg)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")

###Including all investment vs. growth  
* reproducing individuals now plot closer to the "expected line" (as defined by juvenile individuals), but for most species there is still a considerable discrepency
* fit line of veg investment vs. total plant weight through non-reproductive plants
* derive "predicted" total investment (veg+repro) for reproducing individuals
* determine proportional reproductive cost for reproducing individuals; probably look by age

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "total_inv"
xvar <- "total_weight"

@@

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
                    main=spp,col=col.mature(data[[spp]]$mature)
}
#doesn't like preceding lines of text - PROBLEM
###calc_veg <- merge(SummaryInd, select(results, -species), by="species",all.x=TRUE)
###WORK HERE

@@

>>>>

plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
abline(0,1)
text(2.1,3,srt=45,"RA = 0.5")
abline(log10(3),1)
text(2,9,srt=45,"RA = 0.75")
abline(log10(9),1)
text(2,25,srt=45,"RA = 0.9")
abline(log10(19),1)
text(2,60,srt=45,"RA = 0.95")
abline(log10(.111),1)
text(19,3,srt=45,"RA = 0.1")
abline(log10(.010101),1)
text(170,2.4,srt=45,"RA = 0.01")
```

@@

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

@@

mtext("Vegetative investment (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
```

###Including all investment vs. growth  
* reproducing individuals now plot closer to the "expected line" (as defined by juvenile individuals), but for most species there is still a considerable discrepency
* fit line of veg investment vs. total plant weight through non-reproductive plants
* derive "predicted" total investment (veg+repro) for reproducing individuals
* determine proportional reproductive cost for reproducing individuals; probably look by age
*LEES, BOLE, EPMI become much tighter when reproductive investment included - all but 1 species
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "total_inv"
xvar <- "total_weight"

@@

###Calculating cost of reproduction as a growth deficit
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
pdf("figs2/cost_of_repro1.pdf", height=12, width=12)
  plot
par(mfrow=c(1,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
yvar <- "growth_inv"
xvar <- "total_weight"

data <- subset(SummaryInd,repro_inv=0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results_cost <- summarise_all_fits(lmfits)

results_cost$r.squared <- round(results_cost$r.squared,digits=3)
results_cost$p.value <- round(results_cost$p.value,digits=3)
results_cost$a <- round(results_cost$a,digits=2)
results_cost$b <- round(results_cost$b,digits=2)
results_cost

Summary2 <- SummaryInd
Summary2 <- merge(Summary2,select(results_cost, -n), by=c("species"), all=TRUE)

Summary2$predict_growth <- 10^Summary2$a * Summary2$total_weight^Summary2$b
Summary2$cost <- Summary2$predict_growth - Summary2$growth_inv
Summary2$cost_plus_growth <- Summary2$cost + Summary2$growth_inv
Summary2$cost_ratio <- Summary2$predict_growth / Summary2$growth_inv

plot(predict_growth~growth_inv,Summary2,col=col.spp(species),pch=16,log="xy",xlim=c(10,1000000),ylim=c(10,1000000))
abline(0,1)
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

plot(predict_growth~growth_inv,Summary2,log="xy",col=col.age(age),pch=16,xlim=c(10,1000000),ylim=c(10,1000000))
abline(0,1)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")

plot(cost_ratio~RA,Summary2,col=col.spp(species),pch=16,log="y",ylab="ratio of predicted growth to actual growth")
mod <- lm(RA~log(cost_ratio),data=subset(Summary2,RA>0))
words.bottom.left.logy(mod)
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

plot(cost_ratio~RA,Summary2,col=col.age(age),pch=16,log="y",ylab="ratio of predicted growth to actual growth")
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
pdf("figs2/cost_of_repro1.pdf", height=12, width=12)
  plot
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "cost_ratio"
xvar <- "RA"

data <- subset(Summary2,RA>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  ((x[[xvar]]))))
results <- summarise_all_fits(lmfits)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.3,
                    main=spp,col=col.age(data[[spp]]$age))
  }

mtext("ratio of predicted growth to actual growth", 2, outer=TRUE,cex=1.2)
mtext("RA", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "cost"
xvar <- "repro_inv"

data <- subset(Summary2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  ((x[[xvar]]))))
results <- summarise_all_fits(lmfits)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="",xlab="",ylab="",cex=1.3,
                    main=spp,col=col.age(data[[spp]]$age))
  abline(0,1)                  
}

mtext("Growth deficit (mg)", 2, outer=TRUE,cex=1.2)
mtext("Reproductive investment (mg)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

####There is a much less clearcut pattern with respect to height growth - for most species height growth declines dramatically with age, overshadowing any reprodutive maturity affects  
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_height"
xvar <- "height"

mtext("Increase in plant height (mm)", 2, outer=TRUE,cex=1.2)
mtext("Plant height (mm)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

@@

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
                    main=spp,col=col.age(data[[spp]]$age))
}
